---
title: '"Commodities for the Long Run"'
subtitle: "(draft)"
author: "Vito Lestingi"
date: "`r Sys.Date()`"
abstract: "This document includes replication material on some academic and practitioners' literature instrumental for our RGSoC 2020 project. The document itself is meant to be completely reproducible."
output:
  rmarkdown::pdf_document:
    # citation_package: biblatex
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{"Commodities for the Long Run"}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{rmarkdown::render}
editor_options: 
  markdown: 
    wrap: 72
---

1.  

-   Set up for running

```{r, include=FALSE}
rm(list = ls())

options(tinytex.verbose = TRUE)
```

```{r setup, include = FALSE}
knitr::opts_knit$set(
  root.dir = normalizePath('..')
)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  warning = FALSE,
  error = FALSE
)
```

2.  

-   Input quantmod lib
-   Get a excel made by paper author from the path directory The excel
    is recorded as COMLR and it contains data like Excess return of
    equal-weight commodities portfolio for each month from 1877-02 to
    2015-12.
-   Get data from Fred about whether a month is in recession from
    1854-12 to Now

```{r Data sourcing, cache=TRUE}
library(quantmod)

parser.path <- file.path('inst', 'parsers', 'COMLR.R')
source(parser.path)

USREC <- getSymbols.FRED('USREC', auto.assign=FALSE)
index(USREC) <- as.yearmon(index(USREC))
```

3.  

-   Create a function that takes three arguments and returns Arithmetic
    average return, Geometric average return, Volatility and Skewness of
    portofolios
-   The function itself has taken advantages of functions from
    Performance Analytics

```{r Table 2}
CalcReturnMeasures <- function(R, periods, const=100) {
  # @param R An `xts` object with portfolios returns series
  # @param periods A character vector specifying subperiod(s) to subset `R` 
  # @param const A numeric, multiplication constant. Default to 100 used to express percent values
  out <- vector('list', length(periods))
  res <- matrix(NA, 4, ncol(R), 
    dimnames=list(
      c(
        'Arith.Avg.Ret'
        , 'Geom.Avg.Ret'
        , 'Volatility'
        , 'Skewness'
      ),
      colnames(R)
    )
  )
  for (p in 1:length(periods)) {
    COMLR.sub <- R[periods[p], ]
    # Annualized returns
    for (g in c(FALSE, TRUE)) {
      i <- as.integer(g)
      res[i + 1, ] <- PerformanceAnalytics::Return.annualized(
        COMLR.sub, scale=12, geometric=g
      ) * const
    }
    # Volatility
    res[3, ] <- apply(COMLR.sub, 2, function(x) sd(x, na.rm=TRUE) * sqrt(12) * const)
    # Skewness
    res[4, ] <- as.numeric(PerformanceAnalytics::skewness(COMLR.sub, na.rm=TRUE))
    out[[p]] <- res
  }
  names(out) <- periods
  return(out)
}
CalcReturnMeasures(COMLR[, 1:8], periods=c('1877/2020', '1877/2015', '1877/1945', '1946/2015'))
```

4.  

-   Create two charts using chart.CumReturns from PerformanceAnalytics

```{r Figure 2, fig.cap="Equal-weighted Commodity Index Decomposition"}
library(PerformanceAnalytics)

chart.CumReturns(COMLR[,c("XRET.EW","SXRET.EW","CARRY.ADJ.EW")], legend.loc = "topleft", wealth.index = TRUE, geometric = FALSE, main = 'Excess Spot Return/Interest Rate-Adjusted Carry Return \n(cumulative returns %)')

chart.CumReturns(COMLR[,c("XRET.EW","SRET.EW","CARRY.EW")], legend.loc = "topleft", wealth.index = TRUE, geometric = FALSE, main = 'Spot/Carry Return (cumulative returns %)')

```

5.  

-   Create LmHorizon function to perform linear regression with a
    shifting horizon on a dataset.
-   The function initializes an empty list out with a length equal to
    the number of dependent variables specified. It creates a loop that
    iterates through each value in the horizon vector and iterates
    through each dependent variable specified in Y. It then finds the
    index of the current dependent variable y and the current horizon
    h.A if test then assign the independent variable corresponding to
    the current dependent variable.It then shifts the independent
    variable x by h months in the dataset data.Then do a linear
    regression model using the dependent variable y and the shifted
    independent variable x as predictors.Lastly it creates names to the
    output and produce output

```{r Regressions utility function}
LmHorizon <- function(Y, X, horizon, data) {
  # @param Y A character vector, dependent variables. Must be present in `data`, matching column names
  # @param X A character vector, independent variables. Must be present in `data`, matching column names
  # @param horizon A numeric vector, number of months to shift independent variables by
  # @param data An xts object, the data set whose independent variables `X` will be shifted of `horizon`
  out <- vector('list', length(Y))
  for (h in horizon) {
    for(y in Y) {
      i <- match(y, Y)
      j <- match(h, horizon)
      if (is.list(X)) {
        if (length(Y) != length(X)) {
          stop("Y and X must have same length.")
        }
        x <- X[[i]]
      } else {
        x <- X
      }
      data[, x] <- lag(data[, x], h)
      out[[i]][[j]] <- lm(
        formula(paste(y, paste0(x, collapse='+'), sep='~')),
        data=data
      )
      names(out[[i]])[] <- suppressWarnings(
        paste('H', horizon, sep='')
      )
    }
  }
  names(out) <- Y
  return(out)
}
```

6.  

-   The code merges selected columns from COMLR and the USREC dataset,
    limiting the time period to '1878/2015'. The columns selected from
    COMLR are 'XRET.EW' and 'XRET.LS', while the columns selected from
    USREC are labeled 'USREC' and consist of numeric values.

-   It performs linear regressions with a shifting horizon using the
    LmHorizon function. It regresses 'XRET.EW' and 'XRET.LS' on 'USREC',
    'PFC.STATE', and 'INFL.STATE' with three different horizons: 0, 11,
    and 59 months

-   It then run fitTsfm function from factor analysis between 'XRET.EW'
    and 'XRET.LS' and 'USREC', 'PFC.STATE', and 'INFL.STATE'

```{r Table 6 NBER paper}
# Prepare data set
data.macros <- merge(
                     COMLR['1878/2015', c('XRET.EW', 'XRET.LS', 'PFC.STATE', 'INFL.STATE')],
                     'USREC' = as.numeric(USREC['1878/2015'])
)

# Regressions
macro.regs <- LmHorizon(
  Y = c('XRET.EW', 'XRET.LS'), 
  X = c('USREC', 'PFC.STATE', 'INFL.STATE'), 
  horizon = c(0, 11, 59),
  data = data.macros 
)

lapply(unlist(macro.regs, recursive=FALSE), summary)

library(FactorAnalytics)

data.macros_df <- data.frame('Date'=index(data.macros), coredata(data.macros))
data.macros_df$PFC.STATE <- as.factor(data.macros_df$PFC.STATE)
data.macros_df$INFL.STATE <- as.factor(data.macros_df$INFL.STATE)


fitTsfm(asset.names = c("XRET.EW", "XRET.LS"),
        factor.names = c('USREC', 'PFC.STATE', 'INFL.STATE'),
        data=data.macros)
```

## Commodity portfolios and investment styles

7.  

-   Code calculates the value (VAL), momentum (MOM), and carry based on
    the given calculations and data. For value (VAL), it subtracts the
    cumulative sum of rolling 48-month returns from their lagged values
    by 12 months for both equally-weighted (EW) and long-short (LS)
    portfolios.For momentum (MOM), it computes the cumulative sum of
    rolling 12-month returns for both EW and LS portfolios.It then
    merges the calculated values with the relevant columns from COMLR
    dataset and assigns appropriate column names.

-   Code then performs linear regressions with a shifting horizon using
    the LmHorizon function. It regresses XRET.EW and XRET.LS on
    different combinations of MOM, VAL, and PFC.AGG. The regressions are
    performed with three different horizons: 0, 11, and 59 months.

```{r Table 7 NBER paper}
# Value
VAL.EW <- (-1) * lag(PerformanceAnalytics::apply.rolling(COMLR$XRET.EW, 48, cumsum, by=1), 12)
VAL.LS <- (-1) * lag(PerformanceAnalytics::apply.rolling(COMLR$XRET.LS, 48, cumsum, by=1), 12)

# Momentum
MOM.EW <- PerformanceAnalytics::apply.rolling(COMLR$XRET.EW, 12, cumsum, by=1)
MOM.LS <- PerformanceAnalytics::apply.rolling(COMLR$XRET.LS, 12, cumsum, by=1)

# Carry
# measured as the backwardated/contango value of the commodity index
# COMLR$PFC.AGG

data.styles <- merge(
  COMLR['1877/2015', c('XRET.EW', 'XRET.LS', 'PFC.AGG')]
  , VAL.EW
  , VAL.LS
  , MOM.EW
  , MOM.LS
)
colnames(data.styles) <- c(
  'XRET.EW', 'XRET.LS', 'PFC.AGG'
  , 'VAL.EW', 'VAL.LS'
  , 'MOM.EW', 'MOM.LS'
)

# Regressions
style.regs <- LmHorizon(
  Y = c('XRET.EW', 'XRET.LS'), 
  X = list(
    c('MOM.EW', 'VAL.EW', 'PFC.AGG'), 
    c('MOM.LS', 'VAL.LS', 'PFC.AGG')
  ), 
  horizon = c(0, 11, 59),
  data = data.styles
)
lapply(unlist(style.regs, recursive=FALSE), summary)
```

# References
