---
title: "Step 3 Function Identification"
format: html
editor: visual
---

Commodities-long-run has already contained many useful functions that can be used to replicate the paper or offer insights into portofolios that contain commodities

There are the list of functions that worth to be created and documented

-   CalcReturnMeasures --- function that takes three arguments and returns Arithmetic average return, Geometric average return, Volatility and Skewness of portofolios (already in document)

-   LmHorizon --- function that performs linear regressions with a shifting horizon(already in document)

-   CommPortifolio --- a function that can be used to create Table 4 of the paper --- what will happen to Portofolio's mean, violatility, Sharpe Ratio of different period if a certain percentage(10%) of commodities is added

-   CommDrawdown --- a function that can be used to create Table 5 of the paper --- what will happen to Portofolio if 10 worst drawdown happened if a certain percentage(10%) of commodities is added

There is an example of how I want the function to work

A generic CommPortifolio --- assume the investor invests across commodities(Commodities Index)

```{r}
CommPortifolio <- function(R, periods, percentage, const=100) {}
  # @param R An `xts` object with portfolios returns series
  # @param periods A character vector specifying subperiod(s) to subset `R`
  # @param percentage A numberic number that reconstructs the portofolio with X percentage of commodities 
  # @param const A numeric, multiplication constant. Default to 100 used to express percent values
```

A more specific CommPortifolio --- investor invests certain commodities

```{r}
CommPortifolio <- function(R, periods, R1, percentage, const=100) {}
  # @param R An `xts` object with portfolios returns series
  # @param periods A character vector specifying subperiod(s) to subset `R`
  # @param R1 An `xts` object with one or more commodities returns series
  # @param percentage A numberic number that reconstructs the portofolio with X percentage of commodities 
  # @param const A numeric, multiplication constant. Default to 100 used to express percent values
```
